---
title: "mlrng"
output:
  pdf_document:
    toc: true
urlcolor: blue
linkcolor: blue
vignette: >
  %\VignetteIndexEntry{mlrng}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include=FALSE}
library(mlrng)
```
# Building Blocks

The package provides R6 classes for the building blocks of machine learning:

* Tasks
* Learners
* Resamplings
* Performance Measures

All objects are stored in dictionaries (a.k.a. hash maps):
`mlr.tasks` comes with some predefined toy tasks, `mlr.learners` with learners, `mlr.resamplings` with different resampling methods and `mlr.measures` with some popular performance measures.

## Tasks

Here, we first load a predefined task which comes with `mlrng`.
Like most objects in `mlrng`, tasks are stored in a `Dictionary`:
```{r}
print(mlr.tasks)
as.data.table(mlr.tasks)
```
We use the `$get()` function to retrieve the iris task, which is a multiclass classification task:
```{r}
iris.task = mlr.tasks$get("iris")
print(iris.task)
```
Task objects come with some handy self-explanatory getters:
```{r}
# dimension
c(iris.task$nrow, iris.task$ncol)

# name of the target column
iris.task$target

# name of the feature columns
iris.task$features

# formula describing the task
iris.task$formula

# column types
iris.task$col.types

# class levels
iris.task$classes

# number of classes
iris.task$nclasses

# missing values per column
iris.task$missing.values

# complete data
iris.task$data
```

The data itself is stored in an abstract class `Backend`.
It is designed to transparently access in-memory data structures (`data.table` is used internally) as well as real DBMS via the `dplyr` package.
Because most data bases can only be accessed read-only, the operations on these data base backend are limited.
However, you can subset the data to a "view" by excluding rows and columns while the underlying data base must not be altered:
```{r}
# subset to 120 rows and remove column "Petal.Length"
keep = setdiff(c(iris.task$target, iris.task$features), "Petal.Length")
iris.task$subset(rows = 1:120, cols = keep)

iris.task$nrow
iris.task$features
```
Note that you may also alter the data.
In the case of a data base backend, the data is then first fetched from the data base and then stored in a `data.table`.
This affects only the respective rows you operate on.
Thus, if you subsample your data first to only use 0.1% of all observations, you can keep the memory footprint reasonable.


## Learners

All learners are stored in a register called `mlr.learners` and can easily be listed:
```{r}
mlr.learners
as.data.table(mlr.learners)
```

### Dummy classification learner

You can retrieve learners from the dictionary `Learners`:
```{r}
lrn.dummy = mlr.learners$get("classif.dummy")
```

The parameter set is stored in the slot `par.set` and parameters deviating from the default are stored in `par.vals`:
```{r}
lrn.dummy$par.set
lrn.dummy$par.vals
```

Now, we set the parameter `method` to `"sample"`, change the `id` and add the learner to the register:
```{r}
lrn.dummy$par.vals = list(method = "sample")
lrn.dummy$id = "classif.dummy.sample"
mlr.learners$add(lrn.dummy)
as.data.table(mlr.learners)
```
From now on, we can just pass the id `"classif.dummy.sample"` to other functions to use this learner.

### CART

```{r}
lrn.rpart = mlr.learners$get("classif.rpart")
```

## Measures

```{r}
as.data.table(mlr.measures)
measure = mlr.measures$get("mmce")
```

## Resampling

```{r}
mlr.resamplings
as.data.table(mlr.resamplings)
r = mlr.resamplings$get("cv")
print(r)

# change to 3-fold cv
r$iters = 3
```

# Training a model

Here, we fit a simple CART on the iris task:
```{r}
task = mlr.tasks$get("iris")
```


# Resampling

```{r}
rr = resample(task = iris.task, learner = lrn.dummy, resampling = r, measures = list(measure))
rr$data
rr$aggr
```

# Benchmarking

```{r}
tasks = lapply(c("iris", "sonar"), mlr.tasks$get)
learners = lapply(c("classif.dummy", "classif.rpart"), mlr.learners$get)
resamplings = lapply("cv", mlr.resamplings$get)
measures = lapply("mmce", mlr.measures$get)

withr::with_options(list(mlrng.verbose = FALSE), {
  bmr = benchmark(
    tasks = tasks,
    learners = learners,
    resamplings = resamplings,
    measures = measures)
})
bmr$data
```
